|

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Draft of chapter 3

### Added evidental value of including preprints {#sys-rev-including-preprints-res}

@@

Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies. A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist. While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias). Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself. <!-- TODO Read this tool. --> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.

@@

One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region. As covered in the introduction (see Section \@ref(intro-basic-science)), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)). In all cases, excluding these variants attenuates the observed effect to the null. A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]

>>>>

### Added evidential value of including preprints {#sys-rev-including-preprints-res}

@@

Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies. A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist. While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias). Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself. <!-- TODO Read this tool. --> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.

@@

One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region. As covered in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)). In all cases, excluding these variants attenuates the observed effect to the null. A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
